### 2019-08-07 README.Rmd
update readme with preview link

This is the companion repository to the DeepTriangle paper. A preprint can be found at [https://arxiv.org/abs/1804.09253](https://arxiv.org/abs/1804.09253).

>>>>

This is the companion repository to the DeepTriangle paper.

A preview of the current draft can be found at [https://kasaai.github.io/deeptriangle/manuscript.pdf](https://kasaai.github.io/deeptriangle/manuscript.pdf).

A citeable preprint can be found at [https://arxiv.org/abs/1804.09253](https://arxiv.org/abs/1804.09253).
